Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-23 latex/main.tex
Add first pass at authorship

\author[1,\orcidlink{0000-0000-0000-0000}]{First Last}
\author[1,2]{First Middle Last}
\author[2,3]{First M.M. Last}
\author[3,*]{First Last, Jr.}
\author[3,4,5,**]{F. Middle Last}

@@

\affil[1]{University A, London SW7 2AZ, UK}
\affil[2]{Department B, University B, Toronto, ON M5S 3H6, Canada}
\affil[3]{Division C, Department C, University C, Cambridge, MA, USA}

\affil[4]{Senior author}
\affil[5]{Lead contact}

@@

\affil[*]{Correspondence: first.last.jr@university.edu}
\affil[**]{Correspondence: f.middle.last@university.edu}

>>>>

% \author[1,\orcidlink{0000-0000-0000-0000}]{First Last}
% \author[1,2]{First Middle Last}
% \author[2,3]{First M.M. Last}
% \author[3,*]{First Last, Jr.}
% \author[3,4,5,**]{F. Middle Last}

\author[1]{Shing~H.~Zhan}
% TODO add joint second here?
\author[2,3]{Anastasia~Ignatieva}
\author[1]{Yan~Wong}
\author[4]{Katherine~Eaton}
\author[1]{Isobel~Guthrie}
\author[1]{Benjamin~Jeffery}
\author[1]{Duncan~S.~Palmer}
\author[4]{Carmen~Lia~Murall}
\author[5]{Sarah~P.~Otto}
\author[1\orcidlink{0000-0002-7894-5253}]{Jerome~Kelleher}

@@

\affil[1]{Big Data Institute, Li Ka Shing Centre for Health
Information and Discovery, University of Oxford, United Kingdom}
\affil[2]{Department of Statistics, University of Oxford, United Kingdom}
\affil[3]{School of Mathematics and Statistics, University of Glasgow, United Kingdom}
\affil[4]{National Microbiology Laboratory, Public Health Agency of Canada, Canada}
\affil[5]{Department of Zoology and Biodiversity Research Centre, University of British Columbia, Canada}

% \affil[1]{University A, London SW7 2AZ, UK}
% \affil[2]{Department B, University B, Toronto, ON M5S 3H6, Canada}
% \affil[3]{Division C, Department C, University C, Cambridge, MA, USA}

% \affil[4]{Senior author}
% \affil[5]{Lead contact}

@@

%% TODO add correspodning - Shing and Jerome?
\affil[*]{Correspondence: first.last.jr@university.edu}
\affil[**]{Correspondence: f.middle.last@university.edu}
